Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2022-12-20 manuscript/manuscript.tex
Add crystal water pitfalls. Start writing gisttools and pymol intro.

\section{Running GIST}
%\subsection{Running the GIST analysis}
To run a GIST analyis, the following is required:
\begin{itemize}
	\item \software{cpptraj}.
	\item A topology of the molecule of interest in a solvent box.
	\item An MD trajectory of that system.
\end{itemize}
GIST analysis can be divided in three steps: defining a region of interest, running GIST using \software{cpptraj}, and post-processing and analysis.
\cite{Ramsey2016}

@@

\subsubsection{MD simulation}
\todo{Move simulation part from complex to here}
Now, you can run restrained MD simulations based on the equilibrated structures for subsequent GIST analyses.
Restraints should be used during the MD because IST theory is not defined for moving solutes.
We apply a harmonic restraint of \SI{100}{\kilo\calorie\per\mole\per\angstrom\squared} to all heavy atoms to keep the system in place.
We run \SI{100}{\nano\second} of simulation and store the conformations every \SI{100}{\pico\second}.
A simulation length of at least \SI{20}{\nano\second} is recommended to obtain statistically independent snapshots of the water molecules.

@@

\begin{lstlisting}[style=cpptraj]
	parm solvated.parm7
	trajin md-01.nc
	autoimage !(:WAT) origin
	# optionally remove the "pme" option
	gist griddim 100 100 100 out gist.dat \
	refdens 0.03287 pme
\end{lstlisting}
\subsubsection{Interpreting and visualizing the results}

@@

When starting from an experimental structure, care has to be taken during the preparation step.
Make sure to choose a proper protonation state for all titratable moeties.
You will need to solvate your structure in a solvent box, which should be large enough to obtain unbiased long-range electrostatics.
A good criterion for validating the box size is to check whether the water on the outside of the box behaves bulk-like according to the GIST output.

>>>>

\section{Running GIST}
\label{sec:running_GIST}
%\subsection{Running the GIST analysis}
To run a GIST analyis, the following is required:
\begin{itemize}
	\item \software{cpptraj}.
	\item A topology of the molecule of interest in a solvent box.
	\item An MD trajectory of that system.
\end{itemize}
GIST analysis can be divided in three steps: defining a region of interest, running GIST using \software{cpptraj}, and post-processing and analysis.
\cite{Ramsey2016}

@@

\subsubsection{MD simulation}
\todo{Move simulation part from complex to here}
Now, you can run a restrained MD simulation based on the equilibrated structure of biotin for the subsequent GIST analysis.
Restraints should be used during the MD because IST theory is not defined for moving solutes.
We apply a harmonic restraint of \SI{100}{\kilo\calorie\per\mole\per\angstrom\squared} to all heavy atoms to keep the system in place.
We run \SI{100}{\nano\second} of simulation and store the conformations every \SI{100}{\pico\second}.
A simulation length of at least \SI{20}{\nano\second} is recommended to obtain statistically independent snapshots of the water molecules.

@@

\begin{lstlisting}[style=cpptraj]
	parm solvated.parm7
	trajin md-01.nc
	autoimage !(:WAT) origin
	# optionally remove the "pme" option
	gist griddim 100 100 100 out gist.dat \
	refdens 0.03287 pme
\end{lstlisting}
\subsubsection{Interpreting and visualizing the results}
As outlined in section \ref{sec:running_GIST}

@@

When starting from an experimental structure, care has to be taken during the preparation step.
Make sure to choose a proper protonation state for all titratable moeties.

You will need to solvate your structure in a solvent box, which should be large enough to obtain unbiased long-range electrostatics.
A good criterion for validating the box size is to check whether the water on the outside of the box behaves bulk-like according to the GIST output.
Note that due to the solute restraints, some important solvent sites might be unavailable to exchange with the bulk solvent.
Make sure to explicitly place water at such sites, if they are important to the process of interest e.g. waters in confined binding pockets, as they might be missed by automated solvation procedures.
It is good practice to check your restrained MD simulation or solvent populations obtained by GIST afterwards to confirm wether all important solvent sites were properly solvated.
